\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-11-05 demystify.tex
updates

>>>>

\paragraph{Gifts and Professionalism} In many countries, it's customary to give professors gifts, often during holidays.  These gifts can be costly and profs. sometimes expected them. In the US, it's not a common practice, and it's perfectly OK to not to give gifts. \emph{However}, if you'd like to offer small souvenir-like tokens, it's a thoughtful gesture that's appreciated. Some professors proudly display their gifts, which can come from students and colleagues (e.g., when they travel to their home countries or conferences). In summary, small gifts are fine, but avoid anything that might make your professors uncomfortable.

There's a misconception that in the US it's all business, with professors as bosses who pay students for their work, and if you do something nice implies you expect something in return. However, the reality is quite the opposite. While people can be straightforward and direct, they are also friendly and informal. You can call your professor by their first name (\S\ref{sec:address}), respectfully disagree and argue with that (and can actually gain respect doing so), seek their help (even on personal matters), come to their houses for parties or gathering, and give them small thoughtful gifts that they put on their desks.  Many students and professors maintain lifelong relationships, staying in touch through cards, emails, and calls, even after their academic journey ends. These connections are genuine and meaningful.
